## First-Outcome Judgement

<!-- Plot -->

<details>
  <summary>
  Plot - Proportions
  </summary>
  
<br>
  
```{r, out.width = '60%'}
source('r-scripts/exp-1a/fo-recall/fo_recall_filter.R')
source('r-scripts/exp-1a/fo-recall/fo_recall_plots.R')

include_graphics(
  file.path(main_dir,"plots/exp-1a/fo-recall/plt_fo_prop.png")
)
```

Note: 

- Proportions are taken within group and context (High/Low). E.g., All three bars in the top left facet sum to 1, all three bars in the top middle facet sum to 1, and so on.

- Since non-numeric responses were permissible by the experiment's program, data was filtered to remove all non-numeric inputs. If a participant's inputs had a cumulative sum less than 20 or greater than 300, their results were removed.  In total, `r nrow(nr)` participants met this criteria.

<br>

</details>

<details>
  <summary>
    Goodness-of-fit tests - Extreme vs Non-Extreme Reporting
  </summary>
  
```{r}
source('r-scripts/exp-1a/fo-recall/chisq_fo_recall_analysis.R')

chi <- round(c(gf_high_test$statistic, gf_low_test$statistic), 3)
df <- round(c(gf_high_test$parameter, gf_low_test$parameter), 3)
p <- round(c(gf_high_test$p.value, gf_low_test$p.value), 3)
```

<br>

<h4> High Value Result </h4>

$\chi^2(`r df[1]`) = `r chi[1]`, p < 0.001$

<br>

<h4> Low Value Result </h4>  

$\chi^2(`r df[2]`) = `r chi[2]`, p < 0.001$

<br>

</details>  

<details>
  <summary>
    2 $\times$ 3 Chi-Squared Tests - Extreme vs Non-Extreme $\times$ Group
  </summary>

```{r}
chi <- round(c(fo_high_test$statistic, fo_low_test$statistic), 2)
df <- round(c(fo_high_test$parameter, fo_low_test$parameter), 2)
p <- round(c(fo_high_test$p.value, fo_low_test$p.value), 3)
v <- round(c(fo_high_eff, fo_low_eff), 2)
```

<h4> High Value Results </h4>

```{r}
kable(fo_high_tab, 'html', caption = 'High Value Contingency Table') %>%
  kable_classic(full_width = F, position = "left", html_font = "Arial")
```

<br>

$\chi^2(`r df[1]`) = `r chi[1]`, p = `r p[1]`, \varphi_c = `r v[1]`$

- Cannot rule out that recalling the extreme value is independent of group.


```{r}
kable(std_res_high, 'html', caption = 'Standardized Residuals', digits = 3) %>%
  kable_classic(full_width = F, position = "float_left", html_font = "Arial")

kable(p_high, 'html', caption = 'p-values', digits = 3) %>%
  kable_classic(full_width = F, position = "float_left", html_font = "Arial")
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>

None of the three conditions differ significantly from the expected value.

<br>


<h4> Low Value Results </h4>

```{r}
kable(fo_low_tab, 'html', caption = 'Low Value Contingency Table') %>%
  kable_classic(full_width = F, position = "left", html_font = "Arial")
```

<br>

$\chi^2(`r df[2]`) = `r chi[2]`, p = `r p[2]`, \varphi_c = `r v[2]`$

- Cannot rule out that recalling the extreme value is independent of group.


```{r}
kable(std_res_low, 'html', caption = 'Standardized Residuals', digits = 3) %>%
  kable_classic(full_width = F, position = "float_left", html_font = "Arial")

kable(p_low, 'html', caption = 'p-values', digits = 3) %>%
  kable_classic(full_width = F, position = "float_left", html_font = "Arial")
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>

- None of the three conditions differ significantly from the expected value.

<br>

<h4>Post-Hoc Pairwise Fisher-Exact Tests</h4>

```{r}
kable(fish_tests, 'html', digits = 4) %>%
  kable_classic(full_width = F, position = "left", html_font = "Arial")
```

<br>

- Nothing reached significance.  

<br>

Note:

- In the contingency tables, 'Yes' indicates the extreme value was recalled, 'No' indicates that it was not.

- Only recalled outcomes that matched the programmed values were included. i.e., if they saw the *High Value Risky Door*, 80 was logged as "Yes" and 40 was logged as "No." If they saw the *Low Value Risky Door*, 0 was logged as "Yes", 40 was logged as "No". Participants who responded with any "other" values were removed from the analysis. Only Risky doors were evaluated. 

- In total, removing "other" responses resulted `r n_other` participants being excluded from these analyses leaving a final N = `r n_fo`.

- $\varphi_c$ is Cramér’s V, a measure of association for two nominal variables (i.e., an effect size of sorts). It can take a value between 0 and 1, with 0 indicating no association (i.e., full independence). 

- A post-hoc analysis on each $\chi^2$ test was conducted by evaluating the standardized residuals from the chi-square analysis because it seemed the most  natural approach. However, pairwise Fisher Exact tests across the three conditions were also run and is what was reported in the manuscript. The `p_value_adj` column shows corrected p-values using the Holm-Bonferroni method.

<br>

</details>






