## **Risk Preference Trials**

```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1a/risky_trials_filter.R')
```

<!-- Risky Trial Plots -->

<details>
  <summary>
  Plot
  </summary>
  
<br>
  
```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1a/risky_trials_plots.R')
plt_risky_std_blks
```

Errorbars = 95% CI

</details> 

<!-- Main Effects -->

<details>
  <summary>
  Main Effects
  </summary>
  
<br>

```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1a/risky_trials_summary.R')
```

<h3> ANOVA Table </h3>
  
```{r}
kable(risky_main, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

<h3> Conclusions </h3>

**Main Effect of Group:**

$\chi^2(`r df_diffs[2]`) = `r l_rats[2]`, p = `r p_vals[2]`, R^2_N = `r r_sqs[2]`, BF_{10} `r bfs[2]`$

**Main Effect of Choice Value (i.e., Extreme Outcome effect):**

$\chi^2(`r df_diffs[3]`) = `r l_rats[3]`, p `r p_vals[3]`, R^2_N = `r r_sqs[3]`, BF_{10} `r bfs[3]`$

**Main Effect of Block:**

$\chi^2(`r df_diffs[4]`) = `r l_rats[4]`, p = `r p_vals[4]`, R^2_N = `r r_sqs[4]`, BF_{10} `r bfs[4]`$

**Interaction: Group $\times$ Value:**

$\chi^2(`r df_diffs[5]`) = `r l_rats[5]`, p = `r p_vals[5]`, R^2_N = `r r_sqs[5]`, BF_{10} `r bfs[5]`$

**Interaction: Group $\times$ Block:**

$\chi^2(`r df_diffs[6]`) = `r l_rats[6]`, p = `r p_vals[6]`, R^2_N = `r r_sqs[6]`, BF_{10} `r bfs[6]`$

**Interaction: Value $\times$ Block:**

$\chi^2(`r df_diffs[7]`) = `r l_rats[7]`, p `r p_vals[7]`, R^2_N = `r r_sqs[7]`, BF_{10} = `r bfs[7]`$

**Interaction: Group $\times$ Value $\times$ Block:**

$\chi^2(`r df_diffs[8]`) = `r l_rats[8]`, p `r p_vals[8]`, R^2_N = `r r_sqs[8]`, BF_{10} `r bfs[8]`$

<br>

<h4>
Conclusion:
</h4>

There is a 3-way interaction between Group, Value, and Block.

<br>

</details> 


<!-- Relevant Planned Comparisons -->

<details>
  <summary>
  Relevant Planned Comparisons
  </summary>

<h3>
**Comparing Blocks 1 and 3:**
</h3>

<h4>
Block (1 vs 3) $\times$ Group (1 vs 3) $\times$ Value (High vs Low):
</h4>

$b = `r pc_b_val[21]`, t(`r pc_t_df[21]`) = `r pc_t_stat[21]`, p = `r pc_p_val[21]`, r = `r pc_r_val[21]`$

<br>

<h4>
Block (1 vs 3) $\times$ Group (2 vs 3) $\times$ Value (High vs Low):
</h4>

$b = `r pc_b_val[22]`, t(`r pc_t_df[22]`) = `r pc_t_stat[22]`, p = `r pc_p_val[22]`, r = `r pc_r_val[22]`$

<br>

<h4>
Conclusion:
</h4>

The difference between block 1 and 3 significantly interacts with both group and value.

<br>

<h3>
**Comparing Blocks 4 and 6:**
</h3>

<h4>
Block (4 vs 6) $\times$ Group (1 vs 3) $\times$ Value (High vs Low):
</h4>

$b = `r pc_b_val[23]`, t(`r pc_t_df[23]`) = `r pc_t_stat[23]`, p = `r pc_p_val[23]`, r = `r pc_r_val[23]`$

<br>

<h4>
Block (4 vs 6) $\times$ Group (2 vs 3) $\times$ Value (High vs Low):
</h4>

$b = `r pc_b_val[24]`, t(`r pc_t_df[24]`) = `r pc_t_stat[24]`, p = `r pc_p_val[24]`, r = `r pc_r_val[24]`$

<br>

<h4>
Conclusion:
</h4>

The difference between block 4 and 6 significantly interacts with group and value, but only when comparing group 1 and 3 (effect is small). There is no difference comparing group 2 and 3.

<br>

</details> 


<!-- Planned Comparisons Full List -->

<details>
  <summary>
  Planned Comparisons (full list)
  </summary>

<br>

```{r}
kable(risky_pc, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

<br>

</details> 










