## **Risk Preference Trials**

```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1a/risky_trials_filter.R')
```

<!-- Risky Trial Plots -->

<details>
  <summary>
  Plot
  </summary>
  
<br>
  
```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1a/risky_trials_plots.R')
plt_risky_std_blks
```

Errorbars = 95% CI

</details> 

<!-- Risky Trial Main Effects -->

<details>
  <summary>
  Risky Trial Main Effects
  </summary>
  
<br>

```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1a/risky_trials_summary.R')
```

<h3> ANOVA Table </h3>
  
```{r}
kable(risky_main, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

<h3> Conclusions </h3>

**Main Effect of Group:**

$\chi^2(`r df_diffs[2]`) = `r l_rats[2]`, p = `r p_vals[2]`, R^2_N = `r r_sqs[2]`, BF_{10} `r bfs[2]`$

**Main Effect of Choice Value (i.e., Extreme Outcome effect):**

$\chi^2(`r df_diffs[3]`) = `r l_rats[3]`, p `r p_vals[3]`, R^2_N = `r r_sqs[3]`, BF_{10} `r bfs[3]`$

**Main Effect of Block:**

$\chi^2(`r df_diffs[4]`) = `r l_rats[4]`, p = `r p_vals[4]`, R^2_N = `r r_sqs[4]`, BF_{10} `r bfs[4]`$

**Interaction: Group $\times$ Value:**

$\chi^2(`r df_diffs[5]`) = `r l_rats[5]`, p = `r p_vals[5]`, R^2_N = `r r_sqs[5]`, BF_{10} `r bfs[5]`$

**Interaction: Group $\times$ Block:**

$\chi^2(`r df_diffs[6]`) = `r l_rats[6]`, p = `r p_vals[6]`, R^2_N = `r r_sqs[6]`, BF_{10} `r bfs[6]`$

**Interaction: Value $\times$ Block:**

$\chi^2(`r df_diffs[7]`) = `r l_rats[7]`, p `r p_vals[7]`, R^2_N = `r r_sqs[7]`, BF_{10} = `r bfs[7]`$

**Interaction: Group $\times$ Value $\times$ Block:**

$\chi^2(`r df_diffs[8]`) = `r l_rats[8]`, p `r p_vals[8]`, R^2_N = `r r_sqs[8]`, BF_{10} `r bfs[8]`$


</details> 


<!-- Risky Trial Main Effects -->

<details>
  <summary>
  Planned Comparisons
  </summary>

<br>













  
<br>

</details> 










