---
title: "Win Big Results"
# author: "Jeffrey M. Pisklak"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
bibliography: bibTex/refs.bib
csl: bibTex/apa-with-abstract.csl

nocite: |
  @R
---

<!-- https://www.w3schools.com/tags/tag_details.asp -->
<style>
details > summary {
  padding: 4px;
  cursor: pointer;
  font-size: 1.5em;
}

h1.title{font-weight: bold; font-size: 3em}
h1{text-align: left; font-weight: bold; font-size: 2.5em}
h2{text-align: left; font-weight: bold; font-style: italic; font-size: 2em}
h3{text-align: left; font-size: 2em}
h4{text-align: left; font-size: 1.5em}

</style>

```{r setup, include = FALSE}
options(pillar.print_max = Inf)

if (!require(knitr)) {
  install.packages("knitr")
}
if (!require(kableExtra)) {
  install.packages("kableExtra")
}
if (!require(tidyverse)) {
  install.packages("tidyverse")
}

library(knitr)
library(kableExtra)
library(tidyverse)

# Directory
# opts_knit$set(root.dir = dirname(getwd())) #Rendering from this .Rmd file.
opts_knit$set(root.dir = main_dir) # Rendering from generate_markdown.R

opts_chunk$set(
  echo = FALSE,
  # include = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 7, fig.height = 5
)
```

```{r}
# Dependencies
source("r-scripts/prelim_code.R")
```

# **Experiment 1a**

<!-- Contingencies -->

<details>
  <summary>
  Contingencies
  </summary>
  
<br>

<h5>Low Value Options</h5>
- Fixed: 20 (Door 3)
- Risky: 0 or 40 (Door 4)

<h5>High Value Options</h5>
- Fixed: 60 (Door 1)
- Risky: 40 or 80 (Door 2)

<h5>Trials</h5>
- Six blocks of 80 trials.
- *Decision Trials*: (fixed low vs risky low) & (fixed high vs risky high) - 24 per block (12 low, 12 high)
- *Single door trials*: one door to click - 40 per block
- *Catch trials*: high vs low - 16 per block

<h5>EX 80-20</h5>
- Block 1: 80% extreme values (0 low, 80 high)
- Block 2: 50% extreme values.
- Block 3: 20% extreme values (0 low, 80 high)
- Block 4-6: Block 2: 50% extreme values.

<h5>EX 20-80</h5>
- Block 1: 20% extreme values (0 low, 80 high)
- Block 2: 50% extreme values.
- Block 3: 80% extreme values (0 low, 80 high)
- Block 4-6: 50% extreme values.

<h5>EX 50 (control)</h5> 
- All blocks: 50% extreme values.

<br>

  </details>


<!-- Participant Information -->
```{r child = 'markdown/exp-1a/subject_info.Rmd'}
```

<br>

---

<br>

<!-- Catch Trials -->
```{r child = 'markdown/exp-1a/catch_trials.Rmd'}
```

<br>

---

<br>

<!-- Risk Pref Trials -->
```{r child = 'markdown/exp-1a/risk_pref.Rmd'}
```

<br>

---

<br>

<!-- First Outcome Judgement -->
```{r child = 'markdown/exp-1a/fo_recall.Rmd'}
```

<br>

---

<br>

<!-- Frequency Judgement -->
```{r child = 'markdown/exp-1a/freq_judge.Rmd'}
```

<br>

---

<br>

# **Experiment 1b**

<!-- Contingencies -->

<details>
  <summary>
  Contingencies
  </summary>
  
<br>

<h5>Low Value Options</h5>
- Fixed: 20 (Door 3)
- Risky: 0 or 40 (Door 4)

<h5>High Value Options</h5>
- Fixed: 60 (Door 1)
- Risky: 40 or 80 (Door 2)

<h5>Trials</h5>
- Six blocks of 80 trials.
- Decision Trials: (fixed low vs risky low) & (fixed high vs risky high) - 24 per block (12 low, 12 high)
- Single door trials: one door to click - 40 per block
- Catch trials: high vs low - 16 per block

<h5>BEST 80-20</h5>
- Block 1: 80% chance of best outcome on risky options.
- Block 2: 50% of best outcome on risky options.
- Block 3: 20% chance of best outcome on risky options.
- Block 4-6: 50% of best outcome on risky options.

<h5>BEST 20-80</h5>
- Block 1: 20% chance of best outcome on risky options.
- Block 2: 50% of best outcome on risky options.
- Block 3: 80% chance of best outcome on risky options.
- Block 4-6: 50% of best outcome on risky options.

<h5>BEST 50 (control)</h5>
- All blocks: 50% of best outcome on risky options.

<br>

</details>

<!-- Participant Information -->
```{r child = 'markdown/exp-1b/subject_info.Rmd'}
```

<br>

---

<br>


<!-- Catch Trials -->
```{r child = 'markdown/exp-1b/catch_trials.Rmd'}
```

<br>

---

<br>

<!-- Risk Pref Trials -->
```{r child = 'markdown/exp-1b/risk_pref.Rmd'}
```

<br>

---

<br>

<!-- First Outcome Judgement -->
```{r child = 'markdown/exp-1b/fo_recall.Rmd'}
```

<br>

---

<br>

<!-- Frequency Judgement -->
```{r child = 'markdown/exp-1b/freq_judge.Rmd'}
```

<br>

---

<br>

# **R Citations**

`r R.version$version.string`

- ggh4x (`r packageVersion('ggh4x')`) [@ggh4x]
- Hmisc (`r packageVersion('Hmisc')`) [@Hmisc]
- nlme (`r packageVersion('nlme')`) [@nlme]
- RColorBrewer (`r packageVersion('RColorBrewer')`) [@RColorBrewer]
- rcompanion (`r packageVersion('rcompanion')`) [@rcompanion]
- tidyverse (`r packageVersion('tidyverse')`) [@tidyverse]

<br>

---

<br>

# **References**

