## **Risk Preference Trials**

<!-- Risky Trial Plots -->

<details>
  <summary>
    Plot - Block means with 95% CIs
  </summary>
  
<br>
  
```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1b/risky_trials_filter.R')
source('r-scripts/exp-1b/risky_trials_plots.R')
plt_risky_std_blks
```

<br>

</details>


<!-- Main Effects -->

<details>
  <summary>
  Main Effects
  </summary>
  
<br>

```{r, fig.width = 12, fig.height = 6}
source('r-scripts/exp-1b/risky_trials_analysis.R')
source('r-scripts/exp-1b/risky_trials_summary.R')
```

<h4> ANOVA Table </h4>

- Note: All blocks (1 - 6) were included.
  
```{r}
kable(risky_main, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

**Main Effect of Group:**

$\chi^2(`r df_diffs[2]`) = `r l_rats[2]`, p = `r p_vals[2]`, BF_{10} `r bfs[2]`$

**Main Effect of Choice Value (i.e., Extreme Outcome effect):**

$\chi^2(`r df_diffs[3]`) = `r l_rats[3]`, p `r p_vals[3]`, BF_{10} `r bfs[3]`$

**Main Effect of Block:**

$\chi^2(`r df_diffs[4]`) = `r l_rats[4]`, p `r p_vals[4]`, BF_{10} `r bfs[4]`$

**Interaction: Group $\times$ Value:**

$\chi^2(`r df_diffs[5]`) = `r l_rats[5]`, p `r p_vals[5]`, BF_{10} = `r bfs[5]`$

**Interaction: Group $\times$ Block:**

$\chi^2(`r df_diffs[6]`) = `r l_rats[6]`, p `r p_vals[6]`, BF_{10} `r bfs[6]`$

**Interaction: Value $\times$ Block:**

$\chi^2(`r df_diffs[7]`) = `r l_rats[7]`, p `r p_vals[7]`, BF_{10} `r bfs[7]`$

**Interaction: Group $\times$ Value $\times$ Block:**

$\chi^2(`r df_diffs[8]`) = `r l_rats[8]`, p = `r p_vals[8]`, BF_{10} `r bfs[8]`$

<br>

</details>