## Risk Preference Trials

```{r}
source('r-scripts/exp-1b/choice-trials/risk_pref_filter.R')
```

<!-- Risky Trial Plots -->

<details>
  <summary>
    Plot - Block means with 95% CIs
  </summary>
  
<br>
  
```{r, out.width = '100%', out.height = '100%'}
source('r-scripts/exp-1b/choice-trials/risk_pref_plots.R')
include_graphics(
  file.path(main_dir,"plots/exp-1b/choice-trials/plt_risky_blk.svg")
)
```

<br>

</details>

<details>
  <summary>
  Plot - Interaction plot with 95% CIs (Block 5 & 6)
  </summary>

<br>
  
```{r, out.width = '100%', out.height = '100%'}
include_graphics(
  file.path(main_dir,"plots/exp-1b/choice-trials/plt_risky_int.svg")
)
```

<br>

</details>

<details>
  <summary>
  Main Effects
  </summary>
  
```{r}
source("r-scripts/exp-1b/choice-trials/risk_pref_analysis.R")
source('r-scripts/exp-1b/choice-trials/risk_pref_summary.R')
```

<h4> ANOVA Table </h4>
  
```{r}
kable(risky_main, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

**Main Effect of Group:**  
  
$\chi^2(`r df_diffs[2]`) = `r l_rats[2]`, p = `r p_vals[2]`, BF_{10} `r bfs[2]`$

**Main Effect of Choice Value (i.e., Extreme Outcome effect):**

$\chi^2(`r df_diffs[3]`) = `r l_rats[3]`, p `r p_vals[3]`, BF_{10} `r bfs[3]`$
  
**Interaction: Group $\times$ Choice Value:**

$\chi^2(`r df_diffs[4]`) = `r l_rats[4]`, p = `r p_vals[4]`, BF_{10} = `r bfs[4]`$

- Note: while the p-value is technically significant, the Bayes Factor implies the interaction contributes nothing worthwhile.
  
<br>
  
</details>

<details>
  <summary>
  Planned Comparisons
  </summary>
  
<h4> ANOVA Table </h4>

```{r}
kable(pc, 'html', digits = 3) %>%
  kable_classic(full_width = T, position = "center", html_font = "Arial")
```

```{r}
b_vals <- round(pc$Value, 2)
t_stat <- round(pc$`t-value`, 2)
df_vals <- pc$DF
p_vals <- ifelse(pc$`p-value` < 0.001, 
                 '< 0.001', round(pc$`p-value`, 3))
r_vals <- round(pc$r_effect, 2)
```

**BEST 80-20 vs. BEST 50:**

$b = `r b_vals[2]`, t(`r df_vals[2]`) = `r t_stat[2]`, p = `r p_vals[2]`, r = `r r_vals[2]`$

**BEST 20-80 vs. BEST 50:**

$b = `r b_vals[3]`, t(`r df_vals[3]`) = `r t_stat[3]`, p = `r p_vals[3]`, r = `r r_vals[3]`$

**BEST 80-20 vs. BEST 50 | Choice Value (High vs. Low):**

$b = `r b_vals[5]`, t(`r df_vals[5]`) = `r t_stat[5]`, p = `r p_vals[5]`, r = `r r_vals[5]`$

**BEST 20-80 vs. BEST 50 | Choice Value (High vs. Low):**

$b = `r b_vals[6]`, t(`r df_vals[6]`) = `r t_stat[6]`, p = `r p_vals[6]`, r = `r r_vals[6]`$

</details>

<!-- Notes -->

<details>
  <summary>
  Notes
  </summary>

- All plots and analyses are showing the combined effect of block 5 and 6.
- Bayes Factors are reported as Inverse Bayes Factors, this means larger values
indicate greater support for the effect. Anything less than 1 should be considered as contributing no evidence.

</details>